---
title: "Masterscript - Data Preparation"
author: "Hiba Ahmad, Shefali Roy"
date: "`r Sys.Date()`"
output: html_document
---

#Index:
1. Load Packages
2. Prepare Nightlight Data
3. Prepare Census Data
4. Add Sub-district level data on religion and sex
5. Merge Appended Census Data and Nightlight Data
6. Create State-wise Panel Data (2012-2021)

#1. Load Packages

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(Rcpp)
library(raster)
library(sf)
library(haven)
library(tidyr)
library(utils)
library(R.utils)
library(tidyverse)
library(readr)
library(xtable)
library(stargazer)
library(mgcv)
library(ggpubr)
library(ggplot2)
library(plm)
library(countrycode)
library(haven)
library(readr)
library(dplyr)
library(openxlsx)
library(stringr)
library(readxl)
library(data.table)
library(vroom)
```


#2. Prepare Nightlight Data

##Step 1: Prepare Shapefile

###Note: This step requires you to first download the India shapefile from the SHRUG website (https://www.devdatalab.org/shrug_download/shrug_select)

```{r}

# Import India shape file at sub-district level 
ind_shape <- st_read("./Data/Shapefiles/geometries_shrug-v1/subdistrict.shp")

# Convert shape file into an sf object
ind_sf <- as(ind_shape, "sf") 

```


##Step 2: Cut down Global TIFF files to India coordinates (including islands)

###Note 1: This step requires you to first download the the average masked radiance TIFF file for each year from 2012 to 2021 from the Annual VNL V2.1 dataset on Earth Observation Group's website (https://eogdata.mines.edu/nighttime_light/annual/v21/)
###Note 2: Run this chunk only once to save India shaped TIFF files, load those to R for future analysis
###Note 3: Unless you have a super fast computer, run the following chunk manually for each of the 10 global TIFF files for each year from 2012 to 2021 by replacing the name of the file (loop doesn't work). The code for one file is shown below.
 
```{r eval = FALSE}

# Read in the .tif file
tif <- raster("VNL_v21_npp_2021_global_vcmslcfg_c202205302300.lit_mask.dat.tif")

# Set the extent to India (including islands)
india_extent <- extent(62.0, 100.0, 6.0, 37.0)
tif_india <- crop(tif, india_extent)

# Save the cropped image as a new .tif file
writeRaster(tif_india, "india_VNL_v21_npp_2021_global_vcmslcfg_c202205302300.lit_mask.dat.tif", format = "GTiff", overwrite = TRUE)

# Delete the original .tif file
file.remove("VNL_v21_npp_2021_global_vcmslcfg_c202205302300.lit_mask.dat.tif")

```


##Step 3: Extract nightlight radiance values for each year to shapefile

###Note 1: Run this chunk only once to save the dataframes with extracted nightlight values as R objects, load those to R for future analysis 
###Note 2: If you have a super fast computer, you can try using the loop below to do the same more efficiently

```{r eval = FALSE}

# 2012

## Append .tif file into raster data
stack_2012 <- stack(list_2012)

## Extract nightlight intensity on coordinates
data_2012 <- cbind(st_drop_geometry(ind_sf),
                                      raster::extract(stack_2012, ind_shape, fun=mean, df=TRUE, method="bilinear"))

## Rename Layer Column
data_2012 <- data_2012 %>% 
  rename(
    avg_masked_rad_2012 = layer.1,
  )

## Save data frame as an R object
saveRDS(data_2012, "ntl_data_2012.RDS")

## 2013

## Append .tif file into raster data
stack_2013 <- stack(list_2013)

## Extract nightlight intensity on coordinates
data_2013 <- cbind(st_drop_geometry(ind_sf),
                   raster::extract(stack_2013, ind_shape, fun=mean, df=TRUE, method="bilinear"))

## Rename Layer Column
data_2013 <- data_2013 %>% 
  rename(
    avg_masked_rad_2013 = layer.1,
  )

## Save the data frame as an R object
saveRDS(data_2013, "ntl_data_2013.RDS")

## 2014

## Append .tif file into raster data
stack_2014 <- stack(list_2014)

## Extract nightlight intensity on coordinates
data_2014 <- cbind(st_drop_geometry(ind_sf),
                   raster::extract(stack_2014, ind_shape, fun=mean, df=TRUE, method="bilinear"))

## Rename Layer Column
data_2014 <- data_2014 %>% 
  rename(
    avg_masked_rad_2014 = layer.1,
  )

## Save the data frame as an R object
saveRDS(data_2014, "ntl_data_2014.RDS")

## 2015

## Append .tif file into raster data
stack_2015 <- stack(list_2015)

## Extract nightlight intensity on coordinates
data_2015 <- cbind(st_drop_geometry(ind_sf),
                   raster::extract(stack_2015, ind_shape, fun=mean, df=TRUE, method="bilinear"))

## Rename Layer Column
data_2015 <- data_2015 %>% 
  rename(
    avg_masked_rad_2015 = layer.1,
  )

## Save the data frame as an R object
saveRDS(data_2015, "ntl_data_2015.RDS")

## 2016

## Append .tif file into raster data
stack_2016 <- stack(list_2016)

## Extract nightlight intensity on coordinates
data_2016 <- cbind(st_drop_geometry(ind_sf),
                   raster::extract(stack_2016, ind_shape, fun=mean, df=TRUE, method="bilinear"))

## Rename Layer Column
data_2016 <- data_2016 %>% 
  rename(
    avg_masked_rad_2016 = layer.1,
  )

## Save the data frame as an R object
saveRDS(data_2016, "ntl_data_2016.RDS")

## 2017

## Append .tif file into raster data
stack_2017 <- stack(list_2017)

## Extract nightlight intensity on coordinates
data_2017 <- cbind(st_drop_geometry(ind_sf),
                   raster::extract(stack_2017, ind_shape, fun=mean, df=TRUE, method="bilinear"))

## Rename Layer Column
data_2017 <- data_2017 %>% 
  rename(
    avg_masked_rad_2017 = layer.1,
  )

## Save the data frame as an R object
saveRDS(data_2017, "ntl_data_2017.RDS")

## 2018

## Append .tif file into raster data
stack_2018 <- stack(list_2018)

## Extract nightlight intensity on coordinates
data_2018 <- cbind(st_drop_geometry(ind_sf),
                   raster::extract(stack_2018, ind_shape, fun=mean, df=TRUE, method="bilinear"))

## Rename Layer Column
data_2018 <- data_2018 %>% 
  rename(
    avg_masked_rad_2018 = layer.1,
  )

## Save the data frame as an R object
saveRDS(data_2018, "ntl_data_2018.RDS")

## 2019

## Append .tif file into raster data
stack_2019 <- stack(list_2019)

## Extract nightlight intensity on coordinates
data_2019 <- cbind(st_drop_geometry(ind_sf),
                   raster::extract(stack_2019, ind_shape, fun=mean, df=TRUE, method="bilinear"))

## Rename Layer Column
data_2019 <- data_2019 %>% 
  rename(
    avg_masked_rad_2019 = layer.1,
  )

## Save the data frame as an R object
saveRDS(data_2019, "ntl_data_2019.RDS")

## 2020

## Append .tif file into raster data
stack_2020 <- stack(list_2020)

## Extract nightlight intensity on coordinates
data_2020 <- cbind(st_drop_geometry(ind_sf),
                   raster::extract(stack_2020, ind_shape, fun=mean, df=TRUE, method="bilinear"))

## Rename Layer Column
data_2020 <- data_2020 %>% 
  rename(
    avg_masked_rad_2020 = layer.1,
  )

## Save data frame as an R object
saveRDS(data_2020, "ntl_data_2020.RDS")

## 2021

## Append .tif file into raster data
stack_2021 <- stack(list_2021)

## Extract nightlight intensity on coordinates
data_2021 <- cbind(st_drop_geometry(ind_sf),
                   raster::extract(stack_2021, ind_shape, fun=mean, df=TRUE, method="bilinear"))

## Rename Layer Column
data_2021 <- data_2021 %>% 
  rename(
    avg_masked_rad_2021 = layer.1,
  )

## Save data frame as an R object
saveRDS(data_2021, "ntl_data_2021.RDS")

#--------------------------------------

# Loop for Extracting Nightlight Radiance Values for all years together(needs a fast computer)

## Create an empty list to store data frames for each year
#data_list <- list()

## Loop through each year from 2012 to 2021
#for (year in 2012:2021) {

## Create a character vector of file paths for the current year
#file_paths <- list.files(paste0(year), pattern = ".tif$", full.names = TRUE)

## Stack the raster data
#raster_stack <- stack(file_paths)

## Extract mean nightlight intensity values
#extracted_data <- cbind(st_drop_geometry(ind_sf),
#                        raster::extract(raster_stack, ind_shape, fun = mean, df = TRUE, method = "bilinear"))

## Clean column names
#names(extracted_data) <- make.names(names(extracted_data))

## Add the extracted data to the list of data frames
#data_list[[year - 2011]] <- extracted_data
#}

## Merge all data frames into a single data frame
#merged_data <- Reduce(function(x, y) merge(x, y, by = "GID_3"), data_list)

## Export merged data as CSV file
#write.csv(merged_data, "/Users/hibaahmad/Downloads/Hertie/Thesis/Data/India_nightlight_intensity.csv", row.names = FALSE)

```


#Step 4: Compile all R objects to create one nightlight dataset

```{r}

# Create a vector with the years of interest
years <- 2012:2021

# Loop through the years and read the corresponding RDS file
for (year in years) {
  file_path <- paste0("./Data/ntl_data_", year, ".rds")
  assign(paste0("data_", year), readRDS(file_path))
}

# Create a list of data frames
ntl_list <- list(data_2012, data_2013, data_2014, data_2015, data_2016, data_2017, data_2018, data_2019, data_2020, data_2021)

# Merge the data frames by the common columns using a for loop
for (i in 1:(length(ntl_list)-1)) {
  if (i == 1) {
    merged_dataset <- merge(ntl_list[[i]], ntl_list[[i+1]], by = c("pc11_s_id", "pc11_d_id", "pc11_sd_id", "sd_name", "ID"))
  } else {
    merged_dataset <- merge(merged_dataset, ntl_list[[i+1]], by = c("pc11_s_id", "pc11_d_id", "pc11_sd_id", "sd_name", "ID"))
  }
}

```


#3. Prepare Census Data

##Step 1: Load Census data and keys from the SHRUG website (https://www.devdatalab.org/shrug_download/shrug_select)

```{r}

census_data <- read_csv("./Data/csv_shrug-v1/shrug-v1.5.samosa-pop-econ-census-csv/shrug_pc11.csv", show_col_types = FALSE)
census_state_key <- read_csv("./Data/csv_shrug-v1/shrug-v1.5.samosa-keys-csv/shrug_pc11_state_key.csv", show_col_types = FALSE)
census_district_key <- read_csv("./Data/csv_shrug-v1/shrug-v1.5.samosa-keys-csv/shrug_pc11_district_key.csv", show_col_types = FALSE)
census_subdistrict_key <- read_csv("./Data/csv_shrug-v1/shrug-v1.5.samosa-keys-csv/shrug_pc11_subdistrict_key.csv", show_col_types = FALSE)
census_urban_key <- read_csv("./Data/csv_shrug-v1/shrug-v1.5.samosa-keys-csv/shrug_pc11u_key.csv", show_col_types = FALSE)
census_rural_key <- read_csv("./Data/csv_shrug-v1/shrug-v1.5.samosa-keys-csv/shrug_pc11r_key.csv", show_col_types = FALSE)

```

##Step 2: Merge Census data with keys

```{r}

cmerge1 <- left_join(census_state_key, census_data, by = "shrid")
cmerge2 <- left_join(cmerge1, census_district_key, by = c("shrid", "pc11_state_id", "pc11_state_name"))
cmerge3 <- left_join(cmerge2, census_subdistrict_key, by = c("shrid", "pc11_state_id", "pc11_state_name", "pc11_district_id", "pc11_district_name"))
cmerge4 <- left_join(census_rural_key, census_urban_key, by = c("shrid", "pc11_state_id"), multiple = "all")
pop_data <- left_join(cmerge4, cmerge3, by = c("shrid", "pc11_state_id", "pc11_district_id", "pc11_subdistrict_id"), multiple = "all")

```


##Step 3: Clean Census Data

```{r}

#Delete extra columns
pop_data <- subset(pop_data, select = c("shrid", "pc11_state_id", "pc11_district_id", "pc11_subdistrict_id", "pc11_town_id", "pc11_village_id", "pc11_state_name", "pc11_district_name", "pc11_subdistrict_name", "pc11_pca_tot_p", "pc11_pca_tot_p_u", "pc11_pca_tot_p_r", "pc11_pca_p_st", "pc11_pca_p_sc", "pc11_pca_p_lit", "pc11_vd_area", "pc11_vd_power_all_sum", "pc11_vd_power_all_win", "pc11_vd_power_all","pc11_td_area"))

##Rename columns in pop_data
pop_data <- pop_data %>% 
  rename_with(~ str_replace_all(., c(
    "tot_p" = "total_pop",
    "tot_p_u" = "pop_urban",
    "tot_p_r" = "pop_rural",
    "p_st" = "pop_ST",
    "p_sc" = "pop_SC",
    "p_lit" = "pop_literate", 
    "vd_area" = "village_area_hectares", 
    "vd_power_all_sum" = "power_use_all_sum", 
    "vd_power_all_win" = "power_use_all_win", 
    "vd_power_all" = "power_use_all",
    "td_area" = "town_area_sqkms"
  )))

```

##Step 4: Merge Census data with shape file

```{r}

# Make columns lowercase to match the pop_data
ind_sf <- ind_sf %>%
  mutate_at(vars(sd_name), tolower)

# Rename columns in ind_sf
ind_sf <- ind_sf %>% 
  rename_with(~ str_replace_all(., c(
    "pc11_s_id" = "pc11_state_id",
    "pc11_d_id" = "pc11_district_id",
    "pc11_sd_id" = "pc11_subdistrict_id",
    "sd_name" = "pc11_subdistrict_name"
  )))

# Merge census data with shape file
final_pop_data <- left_join(pop_data, ind_sf, by = c("pc11_state_id", "pc11_district_id", "pc11_subdistrict_id", "pc11_subdistrict_name"))

# Rename columns
final_pop_data <- final_pop_data %>% 
  rename_with(~ str_replace_all(., c(
    "pc11_" = "",
    "pca_" = ""
  )))

#keep only states needed - uttar pradesh, rajasthan, gujarat, madhya pradesh
final_pop_data <- final_pop_data %>% 
  filter(state_name %in% c("gujarat", "rajasthan", "madhya pradesh", "uttar pradesh"))

# Remove columns for geometry
final_pop_data <- subset(final_pop_data, select = -c(geometry))

#save as rdata
save(final_pop_data, file = "./Data/pop_data.RData")

# Export merged data as CSV file
#vroom::vroom_write(final_pop_data, file = "./Data/pop_data.csv", delim = ",")
write.csv(final_pop_data, file = "./Data/pop_data.csv", row.names = FALSE)



```


#4. Add Sub-district level data on religion and sex

##Step 1: Prepare data for Rajasthan
```{r state_data}

# Load data
raj <- read_excel("./Data/DDW08C-01 MDDS_Raj.xls")

raj <- raj %>% rename(subdistrict_id = Tehsil,
                       district_id = District,
                      state_id = State)

# Split data by category of total, rural, and urban
  raj1<- dplyr::select(raj, Males, Females, Hindu, Muslim, Other_rel, subdistrict_id, Urban, district_id, state_id, Area_Name) 

 raj1 <- raj1[raj1$Urban == "Total", ] 
 raj2 <- subset(raj1, select = -c(Urban))

# Generate uids - both numeric and string
raj2  <- raj2  %>% mutate(uid = as.numeric(paste0(state_id, district_id, subdistrict_id)))

# Order uid and suid to beginning of dataframe
raj2 <- raj2 %>% dplyr::select(uid, everything())
```

##Step 2: Prepare data for Uttar Pradesh

```{r}

# Load data
up <- read_excel("./Data/DDW09C-01 MDDS_UP.xls")
up <- up %>% rename(subdistrict_id = Tehsil,
                       district_id = District,
                      state_id = State)

# Split data by category of total, rural, and urban
  up1<- dplyr::select(up, Males, Females, Hindu, Muslim, Other_rel, subdistrict_id, Urban, district_id, state_id, Area_Name) 

 up1 <- up1[up1$Urban == "Total", ] 
 up2 <- subset(up1, select = -c(Urban))

# Generate uids - both numeric and string
up2  <- up2  %>% mutate(uid = as.numeric(paste0(state_id, district_id, subdistrict_id)))

# Order uid and suid to beginning of dataframe
up2 <- up2 %>% dplyr::select(uid, everything())

```

##Step 3: Prepare data for Madhya Pradesh

```{r}

# Load data
mp <- read_excel("./Data/DDW23C-01 MDDS_MP.xls")
mp <- mp %>% rename(subdistrict_id = Tehsil,
                       district_id = District,
                      state_id = State)

# Split data by category of total, rural and urban
  mp1<- dplyr::select(mp, Males, Females, Hindu, Muslim, Other_rel, subdistrict_id, Urban, district_id, state_id, Area_Name) 

 mp1 <- mp1[mp1$Urban == "Total", ] 
 mp2 <- subset(mp1, select = -c(Urban))

# Generate uids - both numeric and string
mp2  <- mp2  %>% mutate(uid = as.numeric(paste0(state_id, district_id, subdistrict_id)))

# Order uid and suid to beginning of dataframe
mp2 <- mp2 %>% dplyr::select(uid, everything())

```

##Step 4: Prepare data for Gujarat

```{r}

# Load data
guj <- read_excel("./Data/DDW24C-01 MDDS_Guj.xls")
guj <- guj %>% rename(subdistrict_id = Tehsil,
                       district_id = District,
                      state_id = State)

# Split data by category of total, rural, and urban
  guj1<- dplyr::select(guj, Males, Females, Hindu, Muslim, Other_rel, subdistrict_id, Urban, district_id, state_id, Area_Name) 

 guj1 <- guj1[guj1$Urban == "Total", ] 
 guj2 <- subset(guj1, select = -c(Urban))

# Generate uids - both numeric and string
guj2  <- guj2  %>% mutate(uid = as.numeric(paste0(state_id, district_id, subdistrict_id)))

# Order uid and suid to beginning of dataframe
guj2 <- guj2 %>% dplyr::select(uid, everything())

dplyr::n_distinct(guj2$Area_Name)

n_occur <- data.frame(table(guj2$uid))
guj2[guj2$uid %in% n_occur$Var1[n_occur$Freq > 1],]

```


##Step 5: Append datasets

```{r eval = FALSE}

state_data <- rbind(raj2, up2, mp2, guj2)

write.csv(state_data, file="./Data/State.csv")
#check uniqueness of uid

```


```{r}
state_data <- read.csv("./Data/State.csv")
any(duplicated(state_data$uid))
```

# Note: If values are not unique, i.e., the above returns TRUE, check for duplicate values using the code below
#n_occur <- data.frame(table(state_data$uid))
#duplicate_uid <- n_occur$uid[duplicated(n_occur$uid)]


##Step 6: Clean final_pop_data (created above)

```{r, echo=FALSE}
#read data
data_01 <- read_csv("./Data/pop_data.csv")

# Remove columns for village id, town id, and shrid
data_01 <- subset(data_01, select = -c(village_id, town_id, shrid))

# Remove NAs from state, district, subdistrict, total pop, num households, power use domestic, power use all, power use sum, and power use win columns; not from pop_SC, pop_ST, village area, town area) that are mutually exclusive and would definitely have NAs
data_02 <- data_01[complete.cases(data_01[, c("state_name",  "district_name",  "subdistrict_name" ,   "total_pop" , "power_use_all"   , "power_use_all_sum", "power_use_all_win")]), ]

# Remove duplicate values of villages where values of all population and village area are the same
dup_rows <- duplicated(data_02[, c("district_id", "subdistrict_id","pop_SC", "pop_ST", "total_pop", "village_area_hectares")])

# Subset the data frame to keep only the unique rows
data_03 <- data_02[!dup_rows, ]

#Make all SC, ST, Literate, rural urban NAs O
data_03 <- data_03 %>%
  mutate_at(vars(total_pop_u), ~ifelse(is.na(.), 0, .))

# Remove all cases where pop_sc + pop_st > total-pop at village level
sum(data_03$pop_SC + data_03$pop_ST > data_03$total_pop) #no cases found

#Aggregate to subdistrict level
data_04 <- data_03 %>%
  group_by(state_id, district_id, subdistrict_id, state_name, district_name, subdistrict_name) %>%
  dplyr::summarise(pop_SC = round(sum(pop_SC)),
            pop_ST = round(sum(pop_ST)),
            total_pop = round(sum(total_pop)),
            total_pop_u = round(sum(total_pop_u)),
            total_pop_r = round(sum(total_pop_r)),
            pop_literate = round(sum(pop_literate)),
            village_area_hectares = round(sum(village_area_hectares),2),
            town_area_sqkms = round(sum(town_area_sqkms),2),
            power_use_all_sum = round(mean(power_use_all_sum)),
            power_use_all_win = round(mean(power_use_all_win)),
            power_use_all = round(mean(power_use_all))
            )

# Remove columns for urban and rural population since urban population is very little and for a large part of our sample, rural equals urban
data_05<- subset(data_04, data_04$total_pop_u==0)
data_05 <- subset(data_05, select = -c(total_pop_r, total_pop_u, town_area_sqkms))

# Generate uids - both numeric and string
data_05  <- data_05  %>% mutate(uid = as.numeric(paste0(state_id, district_id, subdistrict_id)))

data_05$suid <- paste(data_05$state_name, data_05$district_name, data_05$subdistrict_name, sep = "-")

# Order suid after uid in df
data_05 <- data_05 %>% dplyr::select(uid, suid, everything())

# Check for duplicates
any(duplicated(data_05$uid))
```

##Step 7: Merge data_05 with state_data for religion and sex (created above)

```{r, echo=FALSE}

merged_pop_data <- merge(data_05, state_data[,c("uid", "Muslim", "Hindu", "Males", "Females", "Other_rel","Area_Name")], by = "uid", all.x=TRUE)


# Rename variables for consistency
merged_pop_data <- merged_pop_data %>% dplyr::rename(pop_male = Males,
                                      pop_female = Females,
                                      pop_hindu = Hindu,
                                      pop_muslim = Muslim,
                                      pop_otherrel = Other_rel)
 
# Reposition variables 
merged_pop_data <- merged_pop_data %>% dplyr::select(uid, suid, Area_Name, everything())
merged_pop_data <- merged_pop_data %>% dplyr::select(uid:pop_literate, pop_muslim:pop_otherrel, everything())
```


##Step 8: Add  variable of other castes to the merged_pop_data

```{r}

# Add a new column for non-SC and non_ST population (total - SC - ST)
merged_pop_data <- merged_pop_data %>%
  mutate(pop_others = total_pop - pop_SC - pop_ST) 

# Check if any other castes except ST SC are negative
any(merged_pop_data$pop_others<0)
sum(merged_pop_data$pop_SC + merged_pop_data$pop_ST > merged_pop_data$total_pop) #no cases found

# Reposition Variables
merged_pop_data <- merged_pop_data %>% dplyr::select(uid:subdistrict_name, total_pop, pop_others, everything())

save(merged_pop_data, file ="./Data/merged_pop_data.RData")
write.csv(merged_pop_data, file =".\\Data\\merged_pop_data.csv", row.names=FALSE)

```

##Step 9: Adjusting male, female, hindu, and muslim populations to the 2011 census using populatoin ratios at subdistrict level

```{r}
#Since the male + female population is greater than total pop, we calculate a new variable called total_pop_mf, then take proportions of male, female, hindu, and muslim from it (assuming the entire population to only be 2 genders), and then use those proportions to append the columns for male, female, hindu, and muslim using the original total_pop variable at subdistrict level

#Pop ratios at subdistrict level - for variables added later
merged_pop_data <- merged_pop_data %>%
  group_by(subdistrict_id) %>%
  mutate(total_pop_mf = sum(pop_male, pop_female),
         male_ratio = pop_male/total_pop_mf,
         female_ratio = pop_female/total_pop_mf,
         otherrel_ratio = pop_otherrel/total_pop_mf,
         hindu_ratio = pop_hindu/total_pop_mf,
         muslim_ratio = pop_muslim/total_pop_mf)

#Pop ratios at state level - for variables added later
merged_pop_data <- merged_pop_data %>%
  group_by(state_name) %>%
  mutate(total_pop_mf = sum(pop_male, pop_female),
         sd_male_ratio = pop_male/total_pop_mf,
         sd_female_ratio = pop_female/total_pop_mf,
         sd_otherrel_ratio = pop_otherrel/total_pop_mf,
         sd_hindu_ratio = pop_hindu/total_pop_mf,
         sd_muslim_ratio = pop_muslim/total_pop_mf)

#Creating new pop muslim and new pop hindu
merged_pop_data <- merged_pop_data %>%
  group_by(subdistrict_id) %>%
  mutate(pop_muslim = round(muslim_ratio*total_pop),
         pop_hindu = round(hindu_ratio*total_pop),
         pop_otherrel = round(otherrel_ratio*total_pop),
         pop_male = round(male_ratio*total_pop),
         pop_female = round(female_ratio*total_pop))


# Creating ratio of population for SC, ST and literate at subd to use later in the construction of panel data - variables from original Census data
merged_pop_data <- merged_pop_data %>%
  mutate(st_ratio = pop_ST/total_pop,
         sc_ratio = pop_SC/total_pop,
         others_ratio = pop_others/total_pop,
         lit_ratio = pop_literate/total_pop)

# Creating ratio of population for SC, ST and literate at subd to use later in the construction of panel data - variables from original census data
merged_pop_data <- merged_pop_data %>%
  group_by(state_name) %>% 
  mutate(sd_st_ratio = pop_ST/sum(total_pop),
         sd_sc_ratio = pop_SC/sum(total_pop),
         sd_others_ratio = pop_others/sum(total_pop),
         sd_lit_ratio = pop_literate/sum(total_pop))


# Creating ratio of subdistrict population to total state population 

merged_pop_data <- merged_pop_data %>%
    group_by(state_name) %>%
  mutate(subdist_ratio = total_pop/sum(total_pop))


```




#5. Merge Appended Census Data and Nightlight Data

##Step 1: Clean Nightlight data

```{r}

# Remove columns for average radiance
ntldata_01 <- subset(merged_dataset, select = -c(avg_rad_2012, avg_rad_2013, avg_rad_2014, avg_rad_2015, avg_rad_2016, avg_rad_2017, avg_rad_2018, avg_rad_2019, avg_rad_2020, avg_rad_2021 ))

#Remove NAs from all columns 
ntldata_02 <- ntldata_01[complete.cases(ntldata_01[, c("pc11_s_id","pc11_d_id", "pc11_sd_id", "sd_name", "avg_masked_rad_2012",  "avg_masked_rad_2013",  "avg_masked_rad_2014" ,   "avg_masked_rad_2015", "avg_masked_rad_2016",   "avg_masked_rad_2017",   "avg_masked_rad_2018"  ,    "avg_masked_rad_2019",        "avg_masked_rad_2020" , "avg_masked_rad_2021")]), ]

##Renaming columns in merged_dataset
ntldata_03 <- ntldata_02 %>% 
  rename_with(~ str_replace_all(., c(
    "pc11_s_id" = "pc11_state_id",
    "pc11_d_id" = "pc11_district_id",
    "pc11_sd_id" = "pc11_subdistrict_id",
    "sd_name" = "pc11_subdistrict_name"
  )))

# Make columns lowercase to match the pop_data
final_ntl_data <- ntldata_03 %>%
  mutate_at(vars(pc11_subdistrict_name), tolower)

# Rename columns
final_ntl_data <- final_ntl_data %>% 
  rename_with(~ str_replace_all(., c(
    "pc11_" = "",
    "pca_" = ""
  )))


## Export merged data as CSV file
write.csv(final_ntl_data, file = "./Data/ntl_data.csv", row.names = FALSE)

```


##Step 2: Merge both datasets

```{r}

thesis_data <- merge(merged_pop_data, final_ntl_data, by = c("state_id", "district_id", "subdistrict_id"), suffixes = c("", ".y"), all.x = TRUE, sort = FALSE)

# Delete the extra column created for subdistrict_name due to some difference in spellings for some of the values
thesis_data <- thesis_data[, !grepl(".y", names(thesis_data))]

# Export merged data as CSV file
write.csv(thesis_data, file = "./Data/thesis_data.csv", row.names = FALSE)
```


#6. Create State-wise Panel Data

##Step 1: Load data

```{r}
pdata <- read.csv("./Data/thesis_data.csv")

```

##Step 2: Create datasets for each year from 2012 to 2021

```{r}

# Loop through years 2012 to 2021 and create datasets with new column year
for (i in 2012:2021) {
  # Create a new dataset with the year column
  pdata_i <- pdata %>% mutate(year = i)
  
  # Assign the new dataset to a variable with the corresponding year
  assign(paste0("pdata_", i), pdata_i)
}

# Add the variable names to the global environment
list2env(setNames(lapply(2012:2021, function(i) get(paste0("pdata_", i))), paste0("pdata_", 2012:2021)), envir = .GlobalEnv)

```

##Step 3: Add total population for each state based on projected values by the Govt of India

```{r}

#Add population data from census report for years 2012-2021
#2012
pdata_2012$total_statepop <- ifelse(pdata$state_name == "rajasthan", 69687000, 
               ifelse(pdata$state_name == "uttar pradesh", 203067000,
                      ifelse(pdata$state_name == "madhya pradesh", 73863000, 61934000)))

#2013
pdata_2013$total_statepop <- ifelse(pdata$state_name == "rajasthan", 70825000, 
               ifelse(pdata$state_name == "uttar pradesh", 206322000,
                      ifelse(pdata$state_name == "madhya pradesh", 75099000, 62877000)))

#2014
pdata_2014$total_statepop <- ifelse(pdata$state_name == "rajasthan", 71963000, 
               ifelse(pdata$state_name == "uttar pradesh", 209577000,
                      ifelse(pdata$state_name == "madhya pradesh", 76334000, 63821000)))

#2015
pdata_2015$total_statepop <- ifelse(pdata$state_name == "rajasthan", 73102000, 
               ifelse(pdata$state_name == "uttar pradesh", 212832000,
                      ifelse(pdata$state_name == "madhya pradesh", 77570000, 64765000)))

#2016
pdata_2016$total_statepop <- ifelse(pdata$state_name == "rajasthan", 74240000, 
               ifelse(pdata$state_name == "uttar pradesh", 216087000,
                      ifelse(pdata$state_name == "madhya pradesh", 78806000, 65698000)))

#2017
pdata_2017$total_statepop <- ifelse(pdata$state_name == "rajasthan", 75248000, 
               ifelse(pdata$state_name == "uttar pradesh", 219051000,
                      ifelse(pdata$state_name == "madhya pradesh", 79948000, 66624000)))

#2018
pdata_2018$total_statepop <- ifelse(pdata$state_name == "rajasthan", 76256000, 
               ifelse(pdata$state_name == "uttar pradesh", 222015000,
                      ifelse(pdata$state_name == "madhya pradesh", 81090000, 67550000)))

#2019
pdata_2019$total_statepop <- ifelse(pdata$state_name == "rajasthan", 77264000, 
               ifelse(pdata$state_name == "uttar pradesh", 224979000,
                      ifelse(pdata$state_name == "madhya pradesh", 82232000, 68476000)))

#2020
pdata_2020$total_statepop <- ifelse(pdata$state_name == "rajasthan", 78273000, 
               ifelse(pdata$state_name == "uttar pradesh", 227943000,
                      ifelse(pdata$state_name == "madhya pradesh", 83374000, 69402000)))

#2021
pdata_2021$total_statepop <- ifelse(pdata$state_name == "rajasthan", 79281000, 
               ifelse(pdata$state_name == "uttar pradesh", 230907000,
                      ifelse(pdata$state_name == "madhya pradesh", 84516000, 70289000)))


```

##Step 4: Add total male population for each state based on projected values by the Govt of India

```{r}

#Add population data from census report for years 2012-2021

#2012
pdata_2012$male_statepop <- ifelse(pdata_2012$state_name == "rajasthan", 36111000, 
               ifelse(pdata_2012$state_name == "uttar pradesh", 106146000,
                      ifelse(pdata_2012$state_name == "madhya pradesh", 38237000, 32308000)))

#2013
pdata_2013$male_statepop <- ifelse(pdata_2013$state_name == "rajasthan", 36670000, 
               ifelse(pdata_2013$state_name == "uttar pradesh", 107812000,
                      ifelse(pdata_2013$state_name == "madhya pradesh", 38862000, 32824000)))

#2014
pdata_2014$male_statepop <- ifelse(pdata_2014$state_name == "rajasthan", 37230000, 
               ifelse(pdata_2014$state_name == "uttar pradesh", 109477000,
                      ifelse(pdata_2014$state_name == "madhya pradesh", 39487000, 33340000)))

#2015
pdata_2015$male_statepop <- ifelse(pdata_2015$state_name == "rajasthan", 37790000, 
               ifelse(pdata_2015$state_name == "uttar pradesh", 111143000,
                      ifelse(pdata_2015$state_name == "madhya pradesh", 40112000, 33856000)))

#2016
pdata_2016$male_statepop <- ifelse(pdata_2016$state_name == "rajasthan", 38350000, 
               ifelse(pdata_2016$state_name == "uttar pradesh", 112809000,
                      ifelse(pdata_2016$state_name == "madhya pradesh", 40737000, 34366000)))

#2017
pdata_2017$male_statepop <- ifelse(pdata_2017$state_name == "rajasthan", 38834000, 
               ifelse(pdata_2017$state_name == "uttar pradesh", 114316000,
                      ifelse(pdata_2017$state_name == "madhya pradesh", 41312000, 34872000)))

#2018
pdata_2018$male_statepop <- ifelse(pdata_2018$state_name == "rajasthan", 39318000, 
               ifelse(pdata_2018$state_name == "uttar pradesh", 115823000,
                      ifelse(pdata_2018$state_name == "madhya pradesh", 41886000, 35378000)))

#2019
pdata_2019$male_statepop <- ifelse(pdata_2019$state_name == "rajasthan", 38803000, 
               ifelse(pdata_2019$state_name == "uttar pradesh", 117330000,
                      ifelse(pdata_2019$state_name == "madhya pradesh", 42460000, 35884000)))

#2020
pdata_2020$male_statepop <- ifelse(pdata_2020$state_name == "rajasthan", 40287000, 
               ifelse(pdata_2020$state_name == "uttar pradesh", 118837000,
                      ifelse(pdata_2020$state_name == "madhya pradesh", 43035000, 36390000)))

#2021
pdata_2021$male_statepop <- ifelse(pdata_2021$state_name == "rajasthan", 40772000, 
               ifelse(pdata_2021$state_name == "uttar pradesh", 120344000,
                      ifelse(pdata_2021$state_name == "madhya pradesh", 43609000, 36872000)))

```

##Step 5: Add total female population for each state based on projected values by the Govt of India

```{r}

#Add female population data from total pop - male pop

for (i in 2012:2021) {
  df_name <- paste0("pdata_", i)
  df <- get(df_name)
  df$female_statepop <- df$total_statepop - df$male_statepop
  assign(df_name, df, envir = .GlobalEnv)
}
```



##Step 6: Assigning different populations by sub-district

```{r}



# Distribution of total population by subdistrict
for (i in 2012:2021) {
  df_name <- paste0("pdata_", i)
  df <- get(df_name) 
  df$total_pop <- round(df$total_statepop * df$subdist_ratio)
  assign(df_name, df, envir = .GlobalEnv)
}
 
# Distribution of ST population by subdistrict
for (i in 2012:2021) {
  df_name <- paste0("pdata_", i)
  df <- get(df_name) 
  df$pop_ST <- round(df$total_statepop * df$sd_st_ratio)
  assign(df_name, df, envir = .GlobalEnv)
}

# Distribution of SC population by subdistrict
for (i in 2012:2021) {
  df_name <- paste0("pdata_", i)
  df <- get(df_name) 
  df$pop_SC <- round(df$total_statepop * df$sd_sc_ratio)
  assign(df_name, df, envir = .GlobalEnv)
}

# Distribution of Others population by subdistrict
for (i in 2012:2021) {
  df_name <- paste0("pdata_", i)
  df <- get(df_name) 
  df$pop_others <- round(df$total_statepop * df$sd_others_ratio)
  assign(df_name, df, envir = .GlobalEnv)
}

# Check if any row exists where pop_SC + pop_ST > total_pop
if (any(pdata$pop_SC + pdata$pop_ST > pdata$total_pop)) {
  # Get the uid for the row(s) that meet the condition
  wrong <- pdata$subdistrict_id[pdata$pop_SC + pdata$pop_ST > pdata$total_pop]
  # Print the uid(s)
  cat("Wrong:\n", wrong, "\n")
} else {
  cat(" ")
}

# Distribution of Muslim population by subdistrict
for (i in 2012:2021) {
  df_name <- paste0("pdata_", i)
  df <- get(df_name) 
  df$pop_muslim <- round(df$total_statepop * df$sd_muslim_ratio)
  assign(df_name, df, envir = .GlobalEnv)
}

# Distribution of Hindu population by subdistrict
for (i in 2012:2021) {
  df_name <- paste0("pdata_", i)
  df <- get(df_name) 
  df$pop_hindu <- round(df$total_statepop * df$sd_hindu_ratio)
  assign(df_name, df, envir = .GlobalEnv)
}


# Distribution of Other religion population by subdistrict
for (i in 2012:2021) {
  df_name <- paste0("pdata_", i)
  df <- get(df_name) 
  df$pop_otherrel <- round(df$total_statepop * df$sd_otherrel_ratio)
  assign(df_name, df, envir = .GlobalEnv)
}


# Distribution of Literate population by subdistrict
for (i in 2012:2021) {
  df_name <- paste0("pdata_", i)
  df <- get(df_name) 
  df$pop_literate <- round(df$total_statepop * df$sd_lit_ratio)
  assign(df_name, df, envir = .GlobalEnv)
}


# Distribution of Male population by subdistrict
for (i in 2012:2021) {
  df_name <- paste0("pdata_", i)
  df <- get(df_name) 
  df$pop_male <- round(df$total_statepop * df$sd_male_ratio)
  assign(df_name, df, envir = .GlobalEnv)
}

# Distribution of Female population by subdistrict
for (i in 2012:2021) {
  df_name <- paste0("pdata_", i)
  df <- get(df_name) 
  df$pop_female <- round(df$total_statepop * df$sd_female_ratio)
  assign(df_name, df, envir = .GlobalEnv)
}


```

##Step 8: Select appropriate nightlight data columns in all panel datasets

```{r}

# Select the appropriate masked radiation column based on the year
pdata_list <- mget(ls(pattern = "^pdata_\\d{4}$"))

pdata_list <- lapply(pdata_list, function(df){
  df %>%
    mutate(ntl_avg_masked_rad = ifelse(year == 2012, avg_masked_rad_2012,
                                ifelse(year == 2013, avg_masked_rad_2013,
                                ifelse(year == 2014, avg_masked_rad_2014,
                                ifelse(year == 2015, avg_masked_rad_2015,
                                ifelse(year == 2016, avg_masked_rad_2016,
                                ifelse(year == 2017, avg_masked_rad_2017,
                                ifelse(year == 2018, avg_masked_rad_2018,
                                ifelse(year == 2019, avg_masked_rad_2019,
                                ifelse(year == 2020, avg_masked_rad_2020,                                                     avg_masked_rad_2021)))))))))) %>%
    dplyr::select(-starts_with("avg_masked_rad_"))
})

# Assign the modified data frames back to their original variables
list2env(pdata_list, envir = .GlobalEnv)

```

##Step 9: Append all panel datasets

```{r}
# Remove redundant panel_i from environment
rm(pdata_i)

#Append all panel datasets
final_panel <- bind_rows(pdata_list)

# Add new row of numbered list of 1 to n for unique number for each observation
final_panel <- tibble::rowid_to_column(final_panel, "NID")
table(final_panel$year)

```

##Step 10: Create categorical variables for all individual panel datasets and the final_panel

```{r}

# Create a list of the dataset names
datasets <- c("final_panel", paste0("pdata_", 2012:2021))

#Loop through the dataframes and create the new categorical variables
for (i in datasets) {
  # Add daily power hours variable
  assign(i, mutate(get(i), daily_power_hours = round((power_use_all_sum + power_use_all_win)/2)))
  
  # Add daily power hours categorical variable
  assign(i, transform(get(i), daily_power_hours_cat = cut(daily_power_hours, breaks=c(0,8,16,24), labels=c("less than 8 hours", "8 to 16 hours", "more than 16 hours"))))
  
  # Add power access (all uses) categorical variable
  assign(i, transform(get(i), power_access = ifelse(power_use_all == 1, "1-power access (all uses)", "0-no power access (all uses)")))
  
  # Convert categorical variables to factors and set reference levels
  assign(i, transform(get(i), daily_power_hours_cat = factor(daily_power_hours_cat, levels=c("less than 8 hours", "8 to 16 hours", "more than 16 hours")),
                       power_access = factor(power_access, levels=c("0-no power access (all uses)", "1-power access (all uses)"))))

}

```

##Step 11: Select appropriate nightlight value range for all individual panel datasets and the final panel

```{r}

for (i in datasets) {
  # Get the data frame associated with the current element of the 'datasets' vector
  df <- get(i)
  
  #Selecting nightlight radiance values 
  ##Check max-min values for nightlight (avg_rad and avg_masked_rad)
  df %>% 
    group_by(year) %>% 
    summarize(min_avg_masked_rad=min(ntl_avg_masked_rad, na.rm=TRUE),
              max_avg_masked_rad=max(ntl_avg_masked_rad, na.rm=TRUE))
  
  ### Subset the data for the average masked radiance variables
  df <- df %>% 
    mutate(ntl_avg_masked_rad = ifelse(ntl_avg_masked_rad > 0 & ntl_avg_masked_rad <= 100, ntl_avg_masked_rad, NA))
  
  # Assign the modified data frame back to the original object
  assign(i, df)
}

summary(final_panel$ntl_avg_masked_rad)
na_df <- final_panel[is.na(final_panel$ntl_avg_masked_rad),]

```


##Step 12: Save all Panel Data Years (2012-2021) & Final Panel Data

```{r}

save(pdata_2012, file ="./Data/Panel_Data_2012.RData")
write.csv(pdata_2012, file ="./Data/Panel_Data_2012.csv", row.names=FALSE)

save(pdata_2013, file ="./Data/Panel_Data_2013.RData")
write.csv(pdata_2013, file ="./Data/Panel_Data_2013.csv", row.names=FALSE)

save(pdata_2014, file ="./Data/Panel_Data_2014.RData")
write.csv(pdata_2014, file ="./Data/Panel_Data_2014.csv", row.names=FALSE)

save(pdata_2015, file ="./Data/Panel_Data_2015.RData")
write.csv(pdata_2015, file ="./Data/Panel_Data_2015.csv", row.names=FALSE)

save(pdata_2016, file ="./Data/Panel_Data_2016.RData")
write.csv(pdata_2016, file ="./Data/Panel_Data_2016.csv", row.names=FALSE)

save(pdata_2017, file ="./Data/Panel_Data_2017.RData")
write.csv(pdata_2017, file ="./Data/Panel_Data_2017.csv", row.names=FALSE)

save(pdata_2018, file ="./Data/Panel_Data_2018.RData")
write.csv(pdata_2018, file ="./Data/Panel_Data_2018.csv", row.names=FALSE)

save(pdata_2019, file ="./Data/Panel_Data_2019.RData")
write.csv(pdata_2019, file ="./Data/Panel_Data_2019.csv", row.names=FALSE)

save(pdata_2020, file ="./Data/Panel_Data_2020.RData")
write.csv(pdata_2020, file ="./Data/Panel_Data_2020.csv", row.names=FALSE)

save(pdata_2021, file ="./Data/Panel_Data_2021.RData")
write.csv(pdata_2021, file ="./Data/Panel_Data_2021.csv", row.names=FALSE)

save(final_panel, file ="./Data/Thesis_Panel.RData")
write.csv(final_panel, file ="./Data/Thesis_Panel.csv", row.names=FALSE)

```

